---
title: "binomial"
author: "Rui Lu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Binomial Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
library(ggplot2)
```

##Brirf introduction to binomial

The package `"binomial"` is a minimal implementation for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.

##The total number of combinations
The following calculations are all based on the functions `bin_choose()`, which takes in arguments `trails` and `success`.
```{r}
bin_choose(n = 5, k = 2)
```

##Probability of binomial random variable

Firstly, you can get the probability of binomial random variable by specifying the arguments, `success`, `trials`, and `prob` for the function `bin_probability()`.

```{r}
#to get probabilities about the 2 successes in 5 random trials performed under probability of 50%
bin_probability(success = 2, trials = 5, prob = 0.5)
```

##Distribution of binomial random variable

Secondly, you can get the distribution of binomial random variable by specifying the arguments, `trials`, and `prob` for the function `bin_distribution()`.

```{r}
#to create a data frame with probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
dis1
```

Then, since the output of this object is of class "bindis", you can plot the probability histogram by calling plot()
```{r}
#to get the probability histogram
plot(dis1)
```

Furthermore, you can also get the cumulative distribution of binomial random variable by specifying the arguments, `trials`, and `prob` for the function `bin_cumulative()`.
```{r}
#to create a data frame with probability distribution and cumulative distribution
dis2 <- bin_cumulative(trials = 5 ,prob = 0.5)
dis2
```

Then, since the output of this object is of class "bindcum", you can plot it by calling plot()
```{r}
# plotting binomial cumulative distribution
plot(dis2)
```

##More information about the binomial distribution

To get the summary about the binomial distribution, you can call the `bin_variable()` function by specifying the arguments `trials` and `prob`. Besides, you can get a nicely printed output by calling `summary()`.
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```

##Summary measures

You can get the summary measures of the binomial distribution by calling the following functions

```{r}
#To get the mean
bin_mean(trials = 10, prob = 0.3)
#To get the variance
bin_variance(trials = 10, prob = 0.3)
#To get the mode
bin_mode(trials = 10, prob =0.3)
#To get the skewness
bin_skewness(trials = 10, prob = 0.3)
#To get the kurtosis
bin_kurtosis(trials = 10, prob = 0.3)
```
