---
output: github_document
---

##Overview

`"binomial"` is a R package that provides functions to calculate probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.

  - `check_trails()` check if an input prob is a valid probability value   
  - `check_prob()` check if an input trials is a valid value for number of trials    
  - `check_success()` check if an input success is a valid value for number of successes   
  - `aux_mean()` calculate the mean   
  - `aux_variance()` calculate the variance   
  - `aux_mode()` calculate the mode   
  - `aux_skewness()` calculate the skewness   
  - `aux_kurtosis()` calculate the kurtosis   
  - `bin_choose()` calculates the number of combinations in which k successes can occur in n trials   
  - `bin_probability()` calculate probabilities about the number of successes in a fixed number of random trials performed under identical conditions    
  - `bin_distribution`; and `plot.bindis()` create a data frame with the probability distribution: sucesses in the first column, probability in the second column    
  - `bin_cumulative`; and `plot.bincum()` create a data frame with both the probability distribution and the cumulative probabilities: sucesses in the first column, probability in the second column, and cumulative in the third column   
  - `bin_var()`; and `print.binvar()`, `summary.binvar()`, `print.summary.binvar()` create a binomial random variable object    
  - `bin_mean()`, `bin_variance()`, `bin_mode()`, `bin_skewness()`, `bin_kurtosis()` calculate the mean, variance, mode, skewness, and kurtosis of binomial distribution
  
##Motivation

This package has been developed to practice the creation of an R package.

## Installation

Install the development version from GitHub via the package `"devtools"`:
```{r results='hide'}
# development version from GitHub:
#install.packages("devtools")

#install "binomial" (with vignettes)

devtools::install_github("stat133-sp19/hw-stat133-AnnRuiLu/workout03/binomial", build_vignettes = TRUE, force = TRUE)
```

##Usage

```{r}
library('binomial')
library(ggplot2)

#check whether it has a valid input probability value
check_prob(0.5)

#check whether it has a valid input of number of trails
check_trials(10)

#check whether it has a valid input of number of success
check_success(1, 2)

#mean
aux_mean(10, 0.3)

#variance
aux_variance(10, 0.3)

#mode
aux_mode(10, 0.3)

#skewness
aux_skewness(10, 0.3)

#kurtosis
aux_kurtosis(10, 0.3)

#the number of combinations in which k successes can occur in n trials
bin_choose(n = 5, k = 2)

#probabilities about the number of successes in a fixed number of random trials performed under identical conditions
bin_probability(success = 2, trials = 5, prob = 0.5)

#create a data frame with the probability distribution: sucesses in the first column, probability in the second column
bin_distribution(trials = 5, prob = 0.5)

#plot probability distribution
plot(bin_distribution(trials = 5, prob = 0.5))

#create a data frame with both the probability distribution and the cumulative probabilities: sucesses in the first column, probability in the second column, and cumulative in the third column
bin_cumulative(trials = 5, prob = 0.5)

#plot cumulative distribution
plot(bin_cumulative(trials = 5, prob = 0.5))

#create a binomial random variable object    
bin_variable(trials = 5, prob = 0.5)

#calculate the mean, variance, mode, skewness, and kurtosis of binomial distribution
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```

